---
title: "Twitter Processing Code"
author: "Robert Turner"
date: "March 5, 2015"
output: html_document
---
```{r global_options, include = FALSE}
knitr::opts_chunk$set(fig.width=5, fig.height=5, fig.align = 'center', message = FALSE, eval = FALSE)
library(streamR)
```
# Usage of Twitter Processing Code:
## Three Main Functions:
1. clean.tweets(tweets)
Does the major processing work on the text. Removes symbols, emoticons, links, and prepares the text for topic modeling. Also processes the date into a correct format if needed.  
  
2. locate.tweets(tweets)
Assigns each tweet a zip code based on its given lattitude / longitude. Only works on geo-located tweets.  
  
3. process.tweets(tweets, variables, languages)
Selects the desired variables / languages of tweets, and does all processing work. Assigns zip codes if possible.
Example:
```{r}
tweets.df = parseTweets("tweets.json", simplify = FALSE)
tweets = process.tweets(tweets.df, vars = c("text", "lang", "created_at"), lan = c("en", "fr"))
```
```{r, echo = FALSE, eval = TRUE}
load("fudge.Rdata")
head(tweets$text)
head(tweets$lang)
head(tweets$created_at)
```

